PANCHANGE_data_preprocessing

### 2020-08-07 PANCHANGE_data_preprocessing2020-07-15.Rmd
I have updated the schizophrenia and bipolar disorder comorbidity chunk, however, there is a problem with the psychotic disorder chunk that needs discussion/fixing

Overlap between self-report schizphrenia and bipolar
+++CH: Check overlap between schizophrenia group and bipolar disorder
++KT: Only 63 with comorbid sel-report bipolar and schizophrenia. More likely to have shared symptoms, less likely to have confirmed diagnoses of both. Could be too severe to be in GLAD?
```{r check bipolar overlap with schizophrenia}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    bipolar_and_schizophrenia_numeric =
      if_else(
        mhd.schizophrenia_numeric == "1" &
          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == "1", 1, 0
      )
  )

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    bipolar_and_schizophrenia =
      recode_factor(bipolar_and_schizophrenia_numeric,
                    "0" = "No comorbid bipoar and schizophrenia",
                    "1" = "Comorbid bipoar and schizophrenia",
                    missing = NA_character_
                    )
  )

glad.mhd.raw.id %>%
  freq(bipolar_and_schizophrenia)
```

>>>>

Overlap between self-report schizophrenia and bipolar disorder
+++CH: Check overlap between schizophrenia group and bipolar disorder
++KT: Only 63 with comorbid self-report bipolar disorder and schizophrenia. More likely to have shared symptoms, less likely to have confirmed diagnoses of both. Could be too severe to be in GLAD?
```{r glad mhd bipolar_and_schizophrenia_numeric}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    bipolar_and_schizophrenia_numeric =
      case_when(
        psychotic_disorders_numeric == 1 &
          mhd.mania_hypomania_bipolar_or_manicdepression == 1 ~ 0,
        psychotic_disorders_numeric == 1 &
          mhd.mania_hypomania_bipolar_or_manicdepression == 1 ~ 1,
        psychotic_disorders_numeric == 1 &
          mhd.mania_hypomania_bipolar_or_manicdepression == 0 ~ 2,
        psychotic_disorders_numeric == 0 &
          mhd.mania_hypomania_bipolar_or_manicdepression == 1 ~ 3
      )
  )

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    bipolar_and_schizophrenia =
      recode_factor(bipolar_and_schizophrenia_numeric,
                    "0" = "No psychotic or bipolar disorder",
                    "1" = "Psychotic and bipolar disorder",
                    "2" = "Only psychotic disorder",
                    "2" = "Only bipolar disorder",
                    missing = NA_character_
                    )
  )

glad.mhd.raw.id %>%
  freq(bipolar_and_schizophrenia,
       cumul = F)
```
